\begin{abstract}	
	Given samples from a set of groups, a data-enriched model describes observations by a common and per-group individual parameters. In high-dimensional regime, each parameter has its own structure such as sparsity or group sparsity.
	In this paper, we consider the general form of data enrichment where data comes in a fixed but arbitrary number of groups $G$ and any convex function, e.g., norm, can characterize the structure of both common and individual parameters.
	We propose an estimator for the high-dimensional data enriched model and investigate its statistical properties. 
	We delineate sample complexity of our estimator and provide high probability non-asymptotic bound for estimation error of all parameters under a condition weaker than the state-of-the-art. 
	We propose an iterative estimation algorithm with a geometric convergence rate and supplement our theoretical analysis with synthetic and real experimental results. 
	In particular, we show the predictive power of data-enriched model along with its interpretable results in anticancer drug sensitivity analysis.    
	Overall, we present a first through statistical and computational analysis of inference in the data enriched model. 
	
	%	Interestingly the sample complexity of our estimator translates to conditions on both per-group sample sizes and the total number of samples. 
%High dimensional structured data enriched model describes groups of observations by shared and per-group individual parameters, each with its own structure such as sparsity or group sparsity.
%In this paper, we consider the general form of data enrichment where data comes in a fixed but arbitrary number of groups $G$.  Any convex function, e.g., norms, can characterize the structure of both shared and individual parameters.
%We propose an estimator for high dimensional data enriched model and provide conditions under which it consistently estimates both shared and individual parameters. 
%We also delineate sample complexity of the estimator and present high probability non-asymptotic bound on estimation error of all parameters. 
%Interestingly the sample complexity of our estimator translates to conditions on both per-group sample sizes and the total number of samples. 
%We propose an iterative estimation algorithm with a linear convergence rate and supplement our theoretical analysis with synthetic and real experimental results. 
%In particular, we show the predictive power of data-enriched model along with its interpretable results in anticancer drug sensitivity analysis.    
\end{abstract}