\section{Restricted Eigenvalue Condition}
\label{sec:re}
The main assumptions of Theorem \ref{theo:deter} is known as Restricted Eigenvalue (RE) condition in the literature of high-dimensional statistics \cite{banerjee14, nrwy12, raskutti10}:
$\inf_{\u \in \cH} \frac{1}{n} \norm{\X \u}{2}^2 \geq \kappa > 0.$
%\be
%\label{eq:recond}
%\inf_{\u \in \cH} \frac{1}{n} \norm{\X \u}{2}^2 \geq \kappa > 0.
%\ee
The RE condition posits that the minimum eigenvalues of the matrix $\X^T \X$ in directions restricted to $\cH$ is strictly positive.
In this section, we show that for the design matrix $\X$ defined in \eqref{eq:x}, the RE condition holds with high probability under a suitable geometric condition we call {\em Data EnRichment Incoherence Condition} (DERIC) and for enough number of samples.
We precisely characterize total and per-group sample complexities required for successful parameter recovery.
For the analysis, similar to existing work \cite{guba16, mend15, trop15}, we assume the design matrix to be isotropic sub-Gaussian.\footnote{Extension to an-isotropic sub-Gaussian case is straightforward by techniques developed in \cite{banerjee14, ruzh13}.}
\begin{definition}
	\label{def:obs}
	We assume $\x_{gi}$ are i.i.d. random vectors from a non-degenerate zero-mean, isotropic sub-Gaussian distribution. In other words, $\ex [\x] = 0$, $\ex [\x^T \x] = \I_{p \times p}$, and $\normth{\x}{\psi_2} \leq k_x$.	
As a consequence, $\exists \alpha > 0$ such that $\forall \u \in \sphere$ we have $ \ex|\langle \x, \u \rangle| \geq \alpha$. Further, we assume noise $\w_{gi} $ are i.i.d.
zero-mean, unit-variance sub-Gaussian with $\normth{\w_{gi}}{\psi_2} \leq k_w$.
\end{definition}

\subsection{Geometric Condition of Recovery}
Unlike standard high-dimensional statistical estimation, for RE condition to be true, parameters of superposition models need to satisfy geometric conditions which limits the interaction of parameters with each other to make sure that recovery is possible. In this section, we elaborate our sufficient geometric condition for recovery and compare it with state-of-the-art condition for recovery of superposition models. 

To intuitively illustrate the necessity of such a geometric condition, consider the simplest superposition model i.e., $\bbeta^*_0 + \bbeta^*_g$. Without any restriction on parameter interactions, any estimates such that $\hbbe_0 + \hbbe_g = \bbeta^*_0 + \bbeta^*_g$ are valid ones. To avoid such trivial solutions two error cones need to satisfy $\ddelta_g \neq -\ddelta_0$. In general, the RE condition of individual superposition models can be established under the so-called Structural Coherence (SC) condition \cite{guba16, mctr13} which is the generalization of this idea for superposition of multiple parameters as $\sum_{g = 0}^{G} \bbeta^*_g$.
 
\begin{definition}[Structural Coherence (SC) \cite{guba16, mctr13}] \label{scc}
	Consider a superposition model of the form $y = \x^T \sum_{g = 0}^{G} \bbeta^*_g + w$. The SC condition requires that
	\be 
	\nr 
	\forall \ddelta_g \in \cC_g, \exists \lambda \quad  \text{s.t.}  \quad \norm{\sum_{g = 0}^{G} \ddelta_g}{2} \geq  \lambda \sum_{g = 0}^{G}  \norm{\ddelta_g}{2},
	\ee  
	and leads to the corresponding RE condition for the superposition model.
\end{definition}

\begin{remark}
	Note that the SC condition is satisfied if none of the individual error cones $\cC_g$ intersect with the inverted error cone $-\cC_0$ \cite{guba16, trop15}, i.e., $\forall g, \alpha_g > 0$ in Figure \ref{fig:sc} where 
	\be 
	\nr 
	\cos(\alpha_g) = \sup_{\ddelta_0 \in \cC_0, \ddelta_g \in \cC_g} -\langle \ddelta_0/\norm{\ddelta_0}{2}, \ddelta_g/\norm{\ddelta_g}{2} \rangle.
	\ee
\end{remark}
Next, we introduce DERIC, a considerably weaker geometric condition compared to SC which leads to recovery of all parameters in the data enriched model. 
\begin{definition}[Data EnRichment Incoherence Condition (DERIC)]  \label{incodef}
	There exists a non-empty set $\cI\subseteq [G]$ of groups where for some scalars $0 < \ratio\leq 1$ and $\lamin>0$ the following holds:
	\begin{enumerate}
		\item $\sum_{i\in \cI} n_i\geq \lceil \ratio n\rceil$.
		\item $\forall i \in \cI$, $\forall \ddelta_i \in \cC_i$, and $\ddelta_0\in\cC_0$: $\norm{\ddelta_i+\ddelta_0}{2}\geq \lamin (\norm{\ddelta_0}{2}+\norm{\ddelta_i}{2})$
	\end{enumerate}
	Observe that $0 < \lamin,\ratio\leq 1$ by definition.
\end{definition}
%\ab{why would $\bar{\rho}=0$ work? also, can $\cI$ be empty? pls update as needed} 

%\ab{add a remark -- so the reader can follow what we are saying}

%\ab{It will be great to have a Figure showing the difference between SC and DERIC.}

\begin{remark}
Comparing to the SC conditions, DERIC holds even if only one of the $\cC_g$s does not intersect with $-\cC_0$. More specifically, DERIC holds if $\exists g, \alpha_g > 0$ in Figure \ref{fig:deric}. Therefore, instead of SC stringent geometric condition, DERIC allows $-\cC_0$ to intersect with an arbitrarily large fraction of the $\cC_g$ cones and as the number of intersections increases, our final error bound becomes looser.
\end{remark}

\subsection{Sample Complexity}
The SC condition on each individual problem fails to utilize the true coupling structure in the data enriched model, where $\bbeta^*_0$ is involved in all groups. In fact, below we show, using SC on each individual model leads to radically pessimistic estimates of the sample complexity for $\bbeta^*_0$ recovery.
\begin{prop}
	\label{prop:super}
	Assume observations distributed as defined in Definition \ref{def:obs} and pair-wise SC conditions are satisfied.  Consider each superposition model \eqref{eq:dirtymodel} in isolation; to recover the common parameter $\bbeta _0^*$ requires at least one group $i$ to have $n_i = O(\omega^2(\cA_0))$. 
	To recover the rest of individual parameters, we need $\forall g \neq i: n_g = O(\omega^2(\cA_g))$ samples. 
	%Recovering the individual parameter $\bbeta^*_g$ needs at least $n_g =  O((\max_{g \in [G]}\omega(\cA_g) + \sqrt{\log 2})^2)$ samples in the group.
\end{prop}
In other words, by separate analysis of superposition estimators at least one problem needs to have sufficient samples for recovering the common parameter $\bbeta_0$ and therefore the common parameter recovery does not benefit from the pooled $n$ samples.
But given the nature of coupling in the data enriched model, we hope to be able to get a better sample complexity specifically for the common parameter $\bbeta_0$.

%\ab{Not sure if I follow this. Assume $g=1$ has sufficient samples, i.e., $n_1 \geq c \omega^2(\cA_0)$. Then, the estimator would proceed in two steps: first, estimate $\beta_0,\beta_1$
%from the first problem; then, use the estimated $\beta_0$ in the other problems to estimate $\beta_2,\ldots,\beta_G$. With such an estimator, we need $n_g \geq c \omega^2(\cA_g), g=2,\ldots,G$.
%So only one problem needs to have sufficient samples.}


%
%Therefore, we have a set of coupled superposition models, and the goal is to estimate their parameters.
%%Another similar model is the one used in \cite{jrsr10}, but the authors are not emphasizing on a distinct common component.
%%As mentioned in Section \ref{sec:introds} the data enriched model can be think of as a coupled set of superposition models.
%The straightforward way to get the sample complexity for satisfying the RE condition is to use results from the superposition literature directly.
%To this end, we need to introduce some preliminary concepts that both previous works and ours build upon.
%
%Secondly to establish the RE condition, shared signal should satisfy an incoherence condition under which we prevent trivial solutions such as $\ddelta_g=-\ddelta_0$ for all $g \in [G]_\setminus$.

 Using DERIC and the small ball method \cite{mend15}, a recent tool from empirical process theory in the following theorem, we get a better sample complexity required for satisfying the RE condition:
\begin{theorem}
	\label{theo:re}
%	Let $\x_{gi}$s be iid, zero-mean, non-degenerate, sub-Gaussian random vector with $\ex [\x_{gi}^T \x_{gi}] = \I_{p \times p}$ and $\vertiii{\x_{gi}}_{\psi_2} \leq k$.
	Let $\x_{gi}$s	be random vectors defined in Definition \ref{def:obs}.
%	Assume that the pair-wise SC conditions of \eqref{def:sc} hold for $\cC_g$s.
	Assume DERIC condition of Definition \ref{incodef} holds for error cones $\cC_g$s and $\rinc=\lamin\ratio/3$.
	Then, for all $\ddelta \in \cH$, when we have enough number of samples as $\forall g \in [G]_{\setminus}: n_g \geq m_g = O(k^6 \alpha^{-6} \rinc^{-2} \omega(\cA_g)^2)$, with probability at least $1 - e^{-n \kappa_{\min}/4}$  we have:
	%as characterized where $-\langle \oomega \ddelta_0 , \D \ddelta_{1:G} \rangle \leq \epsilon \norm{\oomega \ddelta_0}{2} \norm{\D \ddelta_{1:G}}{2}$, therefore we have the following:
	\be
	\nr
	\inf_{\ddelta \in \cH} \frac{1}{\sqrt{n}} \norm{\X \ddelta}{2} &\geq& \frac{\kappa_{\min}}{2}
	\ee
	where $\kappa_{\min} = \min_{g\in [G]_\setminus} C \rinc \frac{\alpha^3}{k^2}  - \frac{2 c_g k \omega(\cA_g)}{\sqrt{n_g}}$ and $\kappa = \frac{\kappa_{\min}^2}{4}$ is the lower bound of the RE condition.
\end{theorem}

\begin{example}
	{\bf ($L_1$-norm)} The Gaussian width of the spherical cap of a $p$-dimensional $s$-sparse vector is $\omega(\cA) = \Theta(\sqrt{s\log p})$ \cite{banerjee14, vershynin2018high}. Therefore, the number of samples per group and total required for satisfaction of the RE condition in the sparse DE estimator \eqref{sde} is $\forall g \in [G]: n_g \geq m_g = \Theta(s_g \log p)$. 
\end{example}



